Analysis of CSV File Reading in R

### 2021-12-09 slides.Rmd
morning

```{r}
mod <- lm(time ~ computer * size * package, data = res)
df <- mod %>% 
  anova() %>% 
  tidy() %>% 
  mutate(across(where(is.numeric), ~ round(.x, 4)))

@@

@@

*   Extend to other forms of data (images, audio)

>>>>

```{r}
mod <- lm(time ~  size * computer * package, data = res)
df <- mod %>% 
  anova() %>% 
  tidy() %>% 
  mutate(across(where(is.numeric), ~ round(.x, 4)))

@@

*   Clearly there's a difference in algorithm reading time when using Mac

```{r, fig.height=2.9, fig.width=4, fig.align='center'}
dat %>% 
  ggplot(aes(size, elapsed, color = meth)) +
  geom_point() +
  geom_smooth(method = "lm", 
              size = 0.5,
              alpha = 0.3) +
  labs(x = "Size (GB)",
       y = "Time Elapsed (sec)",
       color = "Method") +
  scale_color_manual(values = c("midnightblue", "darkgreen", "darkorange2")) +
  theme(axis.title = element_text(size = 9),
        legend.text = element_text(size = 8),
        axis.text = element_text(size = 8),
        legend.title = element_text(size = 9))
```

@@

*   Extend to other file formats (`.tsv`, `.json`...) and other forms of data (images, audio, ...)
